---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gradecalculatorr

<!-- badges: start -->
[![R-CMD-check](https://github.com/UBC-MDS/gradecalculatorr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/UBC-MDS/gradecalculatorr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of gradecalculatorr is to calculate grades for a course. The package allows users to customize their own course information with self-defined course component names, to update grades for different course components, and even understand how well the final exam needs to be to pass the course or achieve a target final grade.


## Installation

You can install the development version of gradecalculatorr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UBC-MDS/gradecalculatorr")
```

## Usage

To get started, we load the library:

```{r setup}
library(gradecalculatorr)
```

Next, let's explore the the function construct_course():  

```{r construct course usingconstruct_course()}
construct_course('dsci524','/') 
#> construct_course('dsci524','/') 
# What is name of dsci524 component #1? lab1
# What is weight percentage of dsci524 component #1? 15
# What is name of dsci524 component #2? lab2
# What is weight percentage of dsci524 component #2? 15
# What is name of dsci524 component #3? lab3
# What is weight percentage of dsci524 component #3? 15
# What is name of dsci524 component #4? lab4
# What is weight percentage of dsci524 component #4? 15
# What is name of dsci524 component #5? quiz1
# What is weight percentage of dsci524 component #5? 20
# What is name of dsci524 component #6? quiz2
# What is weight percentage of dsci524 component #6? 20
#  Components         Weights (%)         Grades (%)
# 1       lab1                 15              <NA>
# 2       lab2                 15              <NA>
# 3       lab3                 15              <NA>
# 4       lab4                 15              <NA>
# 5      quiz1                 20              <NA>
# 6      quiz2                 20              <NA>
```

Then, let's update the grades:

```{r update the grades}
update_component_grade('dsci524.csv', 'lab1', 90.15)
update_component_grade('dsci524.csv', 'lab2', 88.22)
update_component_grade('dsci524.csv', 'lab3', 86.65)
update_component_grade('dsci524.csv', 'lab4', 88.75)
update_component_grade('dsci524.csv', 'quiz1', 90.15)
```

Then, let's calculate how well the quiz2 has to be in order to get 85% total for course 524:

```{r predict quiz2 grade}
predict_final('dsci524.csv', 85)
# > [1] 69.5
```

After quiz2, we know we get 90 for quiz2 and let's calculate the overall grade for course 524:

```{r calculate the overall grade}
update_component_grade('dsci524.csv', 'quiz2', 90.25)
calculate_grade('dsci524.csv')
# > [1] "Course grade is 89.15%"
```
